# Introduction {#intro}

The overall objective of the data analysis and mathematical modeling 
component for the CSU mouse immunology experimental studies is to develop an 
iterative framework to identify key biological components of immunity and to 
quantify their relationships to one another in both data-driven and
mechanistic models for the purpose of evidence-based decision-making for 
tuberculosis (TB) vaccine development. The data sharing plan (DSP) will 
include the experimental data, the quantitative analysis framework, and an 
application programming interface (API) to the results. As detailed in our 
respective biosketches, we have established expertise in all critical 
areas of this data analysis project.


The host immune response to TB vaccination and infection is complex and 
involves interactions between large networks of molecular and cellular 
constituents that vary in time and location within the host. The experimental 
data will be generated from a wide range of measurements and across multiple 
scales; including measures of disease pathology, cellular and chemical 
measurements for cell type and cytokine concentrations, and intracellular 
measurements involving RNA expression and proteomics. The conceptual basis for 
our proposed data analysis and modeling framework is described in a summary
of the recent National Institute of Allergy and Infectious Diseases (NIAID)
workshop, ‘Complex Systems Science, Modeling and Immunity’ [1]. The
major components of this framework are illustrated in Figure 1, where our
approach will integrate experimental data with data-driven modeling to
identify significant correlations and possible causal structures among the  data elements, and with mechanistic modeling of 
cell-mediated immunity that translates biologically-based hypotheses into a 
dynamical system of time-dependent mathematical equations that can be used to 
simulate and test these hypotheses and to inform the design of subsequent experiments.

The proposed work plan begins with the collection and organization of
quantitative and qualitative CSU
generated experimental data that will then be used for data-driven and
mechanistic modeling, with the
analysis results and software modeling tools being made available through a
web-based API. The
milestones of this project are: (1) establishing protocols and standardized
documentation for data
collection and pre-processing from each CSU experimental type, (2) construction
of the relational
database (RDB) for CSU-generated experimental data, (3) collection of
qualitative data describing key
immune features as input for mechanistic modeling, (4) development of
single-type data-driven analysis
tools for each separate experimental system, (5) development of integrated
data-driven analysis tools
for the combined experimental data, (6) development of a dynamical systems model
of cell-mediated
immunity based on qualitative analysis results, (7) development of parameter
estimation and model
calibration procedures for the dynamical systems model, (8) development of
software tools that provide
for a start-to-finish process framework, and (9) development of an API for
public access to relevant data
and results. For each milestone, the gates for Go/No Go decisions will be based
on the positive
reproducibility of the major results by each of the individual CSU
investigators. This approach will ensure
the integration and quality control of each component within the entire
framework.

Immunology data is collected from each CSU mouse experiment as both quantitative
measurements and
qualitative data that includes hypotheses regarding key biological constituents
in the context of TB
vaccine development. An RDB will be developed to provide access and queries to
all combined data
sets. Data-driven modeling will proceed directly from the quantitative data
while mechanistic modeling
will begin with the qualitative data, with the two modeling approaches
increasingly informing each
other as analyses proceed. The data-driven integrated data analysis will include
visualization and
statistical analyses and will also inform parameter estimation for the dynamical
systems model.
Software tools will be developed for all quantitative data and results,
including user testing. A tailored
user interface will provide access to all data and analysis results.


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
